Tampering Detection In Low-Power Smart Cameras

### 2015-05-26 paper.tex
section 3 fino ad outlier detection

\subsection{Related Works}\label{subsec:relWorks}
% Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)
The literature concerning tampering detection is mostly focused on video surveillance applications and operates at few frames per second \gi{Adriano, \'e vero?}. Background models are typically leveraged to identify defocus and occlusions; in particular  ~\cite{aksay2007camera} performs detect defocus \ad{defocus detection?} by analyzing the wavelet domain of each frame and performs histogram comparison for detecting occlusions, while camera displacements are not considered. A background-subtraction technique is employed in~\cite{saglam2009real} to identify defocus, occlusions, and displacements. \gi{FIXME Comparison in the Fourier domain for defocus detection, histogram comparison for occlusion detection, comparison between current background and delayed background for displacement detection}. Background subtraction is also used in \cite{gil2007automatic} to detect defocus, occlusions, and displacements. \gi{FIXME Comparison of edges pixels count for defocus detection, entropy comparison for occlusion detection, block matching algorithm for displacement detection}.
In contrast, no background models are used in \cite{alippi2010detecting}, where a sequential monitoring scheme based on a change-detection test is employed to detect changes in the average gradient energy of each frame to detect defocus due to external disturbances on the camera lens.  
\cite{ribnick2006real}: comparison between frames belonging to a buffer in order to find high values of dissimilarity, associated to tampering.
\cite{kryjak2012fpga}: implementation in a FPGA of a solution based on background modeling, histograms comparisons, edges comparisons.
\cite{harasse2004automated}: tampering detection inside a moving vehicle; uses background subtraction methods in order to identify defocus, occlusions, and displacements. Comparison of edges pixels count for defocus detection, entropy comparison for occlusion detection, block matching algorithm for displacement detection.
\cite{tsesmelis2013tamper}: monitoring of the number of key points extracted by SURF in order to detect defocus events, partition in blocks and HOG descriptors matching for each block in order to detect occlusions. These types of solutions requires a lot of computations
%
%
%
\section{Problem Formulation}\label{sec:probForm}
%
Let $z_t$ be the frame acquired at time $t$, which we model as
\begin{equation}
\label{eq:observationModel}
z_t(x)=\mathcal{D}_t[y_t](x) \quad \forall x \in X
\end{equation}
where $\mathcal{D}_t$ denotes the degradation operator that transforms the original image $y_t$ in the frame $z_t$; $X \subset \mathbb{Z}^2$ denotes the regular pixels grid and $x\in \mathbb{Z}^2$ indicates the pixel coordinates. As far as there is no tampering attacks/events,
\begin{equation}
\label{eq:no_tampering}
\mathcal{D}_t[y_t](x) = y_t(x) + \eta_t(x) \quad \forall x \in X
\end{equation}
where $\eta_t$ is a random variable accounting for different noise sources (e.g., thermal, quantization, photon-counting). In normal conditions, all the images $y_t$ (thus also the frames $z_t$) might show different content but are acquired from the same viewpoint and the same camera orientation.

@@

To obtain indicators that in normal conditions can be treated as i.i.d. realizations of a random variable we detrend~\cite{Gustafsson2000} the indicator sequence by performing temporal derivative
\begin{equation}\label{eq:detrending}
 \partial l_k(t) = l_k(t)-l_k(t-1),  \ \ k = 1, \dots, K\,,
\end{equation}
and we similarly define $\partial g(t)$. Detrended indicators are more suitable to be monitored by a confidence interval since, as shown in Figure REFERENCE\_TODO.b). However, a tampering yielding permanent changes in the indicators, as those in Figure REFERENCE\_TODO.a results in a single outlier in the detrended indicator~\eqref{eq:detrending}.

@@

	\textbf{Operational phase}:\\
	\lnl{DISPL-Test1} \For{$t=T_{o} + 1,\dots,\infty$}{
		\lnl{DISPL-Test2} Get frame $z_t$, set $n_l =0$
		\lnl{DISPL-Test4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Test5} Compute $\partial l_k(t)$\\
			\lnl{DISPL-Test6} \If{$\partial l_k(t) < -\gamma \sigma_{l_k} \vee \partial l_k(t) > \gamma \sigma_{l_k} $}{
				\lnl{DISPL-Test7} $n_l=n_l+1$\\
			}
		}
		\lnl{DISPL-Test8} \If{$n_l\geq K-1$}{
			\lnl{DISPL-Test9} tampering (probably displacement or occlusion) has occurred in $z_t$ \\
		}
		\lnl{DISPL-Test10} Compute $\partial g(t)$\\
		\lnl{DISPL-Test11} \If{$\partial g(t) < -\gamma \sigma_{g} \vee \partial l(t) > \gamma \sigma_{g} $}{
				\lnl{DISPL-Test9} tampering (probably out-of-focus) has occurred in $z_t$ \\
								}

	}   
	\caption{The Proposed Tampering-Detection Algorithm}
	\label{alg:DISPL}
\end{algorithm}

@@

%\begin{equation}
%\label{eq:energyLuma}
%l(t) = \mathcal{L}[z_t] =\frac{\sum_{\mathcal{X}} z_t(x) }{|\mathcal{X}|} ,
%\end{equation}  
%
%
%\begin{equation}
%\label{eq:gradientDetr}
%\frac{\partial g}{\partial t}(t) = g(t) - g(t-1),
%\end{equation}
%
%
%\begin{equation}
%\label{eq:lumaDetr}
%\frac{\partial l}{\partial t}(t) = l(t) - l(t-1).
%\end{equation}

\subsection{Outlier Detection}\label{subsec:MonitoringScheme}

\begin{equation}
\label{eq:soglieGradiente}
\begin{array}{lcl}
\Gamma_{min}^k & = & \hat{\mu}_g^k -\gamma \hat{\sigma}_g^k\\
\Gamma_{max}^k & = & \hat{\mu}_g^k + \gamma \hat{\sigma}_g^k
\end{array},
\end{equation}
dove $\hat{\mu}_g^k$ indica il valore medio delle osservazioni del training set
\begin{equation}
\hat{\mu}_g^k = \frac{\sum_{\tau = 1}^{T_{o}} \frac{\partial g^k}{\partial t}(\tau)}{T_{o}}, \nonumber
\end{equation}
$\hat{\sigma}_g^k$ indica la deviazione standard delle osservazioni del training set
\begin{equation}
\hat{\sigma}_g^k  = \sqrt{\frac{1}{T_{o}-1}\sum_{\tau=1}^{T_{o}}\left(\frac{\partial g^k}{\partial t}(\tau) - \hat{\mu}_g^k(\tau)\right)^2} \nonumber
\end{equation}
e $\gamma>1$ \`e un parametro moltiplicativo ottenuto sperimentalmente.\\

\begin{equation}
\label{eq:soglieLuma}
\begin{array}{rcl}
\Gamma_{min}^k & = & \hat{\mu}_l^k -\gamma \hat{\sigma}_l^k\\
\Gamma_{max}^k & = & \hat{\mu}_l^k + \gamma \hat{\sigma}_l^k
\end{array},
\end{equation}
dove $\hat{\mu}_l^k$ indica il valore medio delle osservazioni del training set
\begin{equation}
\hat{\mu}_l^k = \frac{\sum_{\tau = 1}^{T_{o}} \frac{\partial l^k}{\partial t}(\tau)}{T_{o}}, \nonumber
\end{equation}
$\hat{\sigma}_l^k$ indica la deviazione standard delle osservazioni del training set
\begin{equation}
\hat{\sigma}_l^k  = \sqrt{\frac{1}{T_{o}-1}\sum_{\tau=1}^{T_{o}}\left(\frac{\partial l^k}{\partial t}(\tau) - \hat{\mu}_l^k(\tau)\right)^2} \nonumber
\end{equation}
e $\gamma>1$ \`e un parametro moltiplicativo ottenuto sperimentalmente.\\

\subsection{Algorithm Summary}\label{subsec:AlgorithmSummary}

%\begin{algorithm}[tp]
%	% \SetAlgoNoLine
%	\LinesNumbered
%	\SetAlgoNlRelativeSize{0}
%	\SetNlSty{small}{}{.}
%	\textbf{Configuration}:\\
%	\lnl{DEF-Tr0} Extract regions $\{R_k\}, k=1,\dots,K$  \\
%	\lnl{DEF-Tr1} \For{$t=1,\dots,T_{o}$}
%	{	\lnl{DEF-Tr2} Acquire frame $z_t$ \\
%		\lnl{DEF-Tr2a} \For{$k=1,\dots,K$}{
%			\lnl{DEF-Tr3a} Compute $g^k(t)$, $\frac{\partial g^k}{\partial t}(t)$ for the region $R_k$\\
%		}
%		\lnl{DEF-Tr3} Compute $g(t)$, $\frac{\partial g}{\partial t}(t)$ \\
%	}
%	\lnl{DEF-Tr6a} \For{$k=1,\dots,K$}{
%		\lnl{DEF-Tr7a} Define thresholds $\Gamma_{min}^k$ and $\Gamma_{max}^k$\\
%	}
%	\lnl{DEF-Tr5} Define CDT parameters on $g(t)$ variance\\
%	\textbf{Operational phase}:\\
%	\lnl{DEF-Test1} \For{$t=T_{o},\dots,\infty$}{
%		\lnl{DEF-Test2} Acquire frame $z_t$ \\
%		\lnl{DEF-Tr3b} Compute $g(t)$, $\frac{\partial g}{\partial t}(t)$ \\
%		\lnl{DEF-Test2a} $n=0$\\
%		\lnl{DEF-Test4a} \For{$k=1,\dots,K$}{
%			\lnl{DEF-Test5a} Compute $g^k(t)$, $\frac{\partial g^k}{\partial t}(t)$ for the region $R_k$\\
%			\lnl{DEF-Test6a} \If{$\frac{\partial g^k}{\partial t}(t) < \Gamma_{min}^k \vee \frac{\partial g^k}{\partial t}(t) > \Gamma_{max}^k $}{
%				\lnl{DEF-Test7a} $n=n+1$\\
%			}
%		}
%		\lnl{DEF-Test81} \If{$n \geq K-1$}{
%			\lnl{DEF-Test91} $z_t$ is a defocused frame\\
%		}
%		\lnl{DEF-Test8} \If{CDT detect a change on $g(t)$ variance}{
%			\lnl{DEF-Test9} $z_t$ is a defocused frame\\
%		}
%	}   
%	\caption{Blur detection algorithm}
%	\label{alg:DEFOCUS}
%\end{algorithm}

%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}

>>>>

\subsection{Related Works}\label{subsec:relWorks}
% Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)
The literature concerning tampering detection is mostly focused on video surveillance applications and operates at few frames per second \gi{Adriano, \'e vero?}. Background models are typically leveraged to identify defocus and occlusions; in particular~\cite{aksay2007camera} performs defocus detection by analyzing the wavelet domain of each frame and performs histogram comparison for detecting occlusions, while camera displacements are not considered. A background-subtraction technique is employed in~\cite{saglam2009real} to identify defocus, occlusions, and displacements. \gi{FIXME Comparison in the Fourier domain for defocus detection, histogram comparison for occlusion detection, comparison between current background and delayed background for displacement detection}. Background subtraction is also used in \cite{gil2007automatic} to detect defocus, occlusions, and displacements. \gi{FIXME Comparison of edges pixels count for defocus detection, entropy comparison for occlusion detection, block matching algorithm for displacement detection}.
In contrast, no background models are used in \cite{alippi2010detecting}, where a sequential monitoring scheme based on a change-detection test is employed to detect changes in the average gradient energy of each frame to detect defocus due to external disturbances on the camera lens.  
\cite{ribnick2006real}: comparison between frames belonging to a buffer in order to find high values of dissimilarity, associated to tampering.
\cite{kryjak2012fpga}: implementation in a FPGA of a solution based on background modeling, histograms comparisons, edges comparisons.
\cite{harasse2004automated}: tampering detection inside a moving vehicle; uses background subtraction methods in order to identify defocus, occlusions, and displacements. Comparison of edges pixels count for defocus detection, entropy comparison for occlusion detection, block matching algorithm for displacement detection.
\cite{tsesmelis2013tamper}: monitoring of the number of key points extracted by SURF in order to detect defocus events, partition in blocks and HOG descriptors matching for each block in order to detect occlusions. These types of solutions requires a lot of computations
%
%
%
\section{Problem Formulation}\label{sec:probForm}
%
Let $z_t$ be the frame acquired at time $t$, which we model as
\begin{equation}
\label{eq:observationModel}
z_t(x)=\mathcal{D}_t[y_t](x) \quad \forall x \in X
\end{equation}
where $\mathcal{D}_t$ denotes the degradation operator that transforms the original image $y_t$ in the frame $z_t$; $X \subset \mathbb{Z}^2$ denotes the regular pixels grid and $x\in \mathbb{Z}^2$ indicates the pixel coordinates. As far as there is no tampering attacks/events,
\begin{equation}
\label{eq:no_tampering}
\mathcal{D}_t[y_t](x) = y_t(x) + \eta_t(x) \quad \forall x \in X
\end{equation}
where $\eta_t$ is a random variable accounting for different noise sources (e.g., thermal, quantization, photon-counting). In normal conditions, all the images $y_t$ (thus also the frames $z_t$) might show different content but are acquired from the same viewpoint and the same camera orientation.

@@

To obtain indicators that in normal conditions can be treated as i.i.d. realizations of a random variable we, detrend~\cite{Gustafsson2000} the indicator sequence by a temporal derivative
\begin{equation}\label{eq:detrending}
 \partial l_k(t) = l_k(t)-l_k(t-1),  \ \ k = 1, \dots, K\,,
\end{equation}
and we similarly define $\partial g(t)$. Detrended indicators are more suitable to be monitored by a confidence interval since, as shown in Figure REFERENCE\_TODO.b). However, a tampering yielding permanent changes in the indicators, as those in Figure REFERENCE\_TODO.a results in a single outlier in the detrended indicator~\eqref{eq:detrending}.

We perform outlier detection by defining confidence regions for our indicator in tampering-free frames. In practice, since all these are scalar indicators, it is enough to compute the indicator mean ($\overline{\partial l}_k(t), k = 1,\dots,K$ and $\overline{\partial g}(t)$) and standard deviations ($\sigma_{l_k}, k = 1,\dots,K$ and $\sigma_g$) over the tampering-free frames provided for training, namely $z_t\,, t = 1, \dots, T_o$. Confidence regions are then defined as 
\begin{equation}\label{eq:confidenceRegions}
 [\overline{\partial l}_k(t) - \gamma \sigma_{l_k}, \overline{\partial l}_k(t) + \gamma \sigma_{l_k}],  k = 1,\dots,K
\end{equation}
where $\gamma >0$ is a tuning parameter. A similar region is built for $\partial g$. During operations, any indicator falling outside the corresponding confidence region is considered anomalous and tampering is detected.

@@

	\textbf{Operational phase}:\\
	\lnl{DISPL-Test1} \For{$t=T_{o} + 1,\dots,\infty$}{
		\lnl{DISPL-Test2} Get frame $z_t$, set $n_l =0$
		\lnl{DISPL-Test4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Test5} Compute $\partial l_k(t)$\\
			\lnl{DISPL-Test6} \If{$\partial l_k(t) < -\gamma \sigma_{l_k} \vee \partial l_k(t) > \gamma \sigma_{l_k} $}{
				\lnl{DISPL-Test7} $n_l=n_l+1$\\
			}
		}
		\lnl{DISPL-Test8} \If{$n_l\geq K-1$}{
			\lnl{DISPL-Test9} tampering (probably displacement or occlusion) has occurred in $z_t$ \\
		}
		\lnl{DISPL-Test10} Compute $\partial g(t)$\\
		\lnl{DISPL-Test11} \If{$\partial g(t) < -\gamma \sigma_{g} \vee \partial l(t) > \gamma \sigma_{g} $}{
				\lnl{DISPL-Test9} tampering (probably out-of-focus) has occurred in $z_t$ \\
								}
	}   
	\caption{The Proposed Tampering-Detection Algorithm}
	\label{alg:DISPL}
\end{algorithm}

@@
